\sysfull

### 2017-08-06 paper/coalescing.tex
add some coalescing results

\begin{figure}
	\centering
	%\includegraphics[width=\columnwidth]{figures/task_coalescing}
	\caption{Task coalescing architecture.}
	\label{fig:}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalescing}
	\caption{This figure shows the performance of \sys when it uses the dynamic tasks coalescing mechanism as compared to its performance when the virtual task size is fixed to one, on multiple distances. }
	\label{fig:coalescing}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/averageVirtualTaskSize}
	\caption{ This figure shows the average virtual task size (measured in real task unit) of the virtual task sizes that the coalescing algorithm used to accomplished the applications on a distance of 60cm. }
	\label{fig:aveVirtuTaskSize}
\end{figure}
